---
title: "QNM Sensitivity Analysis"
author: "M Fisher"
date: "2023-07-12"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

## Description 

This RMarkdown explores QNM sensitivity - how sensitive variable responses are to each link in the QNM, under a HAB perturbation.

The focus of the sensitivity analysis is the Status Quo QNM. There are two methods of assessing model sensitivity that we explored:

1. Boosted Regression Trees (BRTs) based on Melbourne-Thomas et al. (2012): https://esapubs.org/archive/mono/M082/019/tree.r

2. Edge strength based on Magel & Francis (2023)

For edge strength (because it's a pretty fast and easy summary) we'll also look into the eight adaptation QNMs. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)

#---- libraries ----
library(here)
library(tidyverse)
library(ggplot2)
#Load XML first--dependency not included in QPress
#To install QPress: 
#   library(remotes)
#   remotes::install_github("SWotherspoon/QPress")
library(XML)
library(tcltk2)
library(gridExtra)
library(cowplot)
library(QPress)

library(igraph)
# library(gbm)
# library(dismo)

#---- custom functions ----
source(here('R','parse.constraints.SWotherspoon.R'))
source(here('R','qnm.sensitivity.R'))
source(here('R','impact.ss.R'))
```



## Data

Read in a variable key. 
```{r}
sqkey <- read_csv(here('data','sq_variable_key.csv'), col_names=TRUE)

# add a hab variable to the key
sqkey <- sqkey %>%
  bind_rows(data.frame(variable="HAB",group="ecosystem"))

# save a subset of the variables in a new data frame -- only well-being and capacity variables
subvars <- sqkey %>% filter(group %in% c("well-being","well-being 2","well-being 3","capacity")) %>%
  arrange(2)
```

Status Quo model and simulations:
```{r echo=TRUE}
#---- Dia Model ---- 
m.sq <- model.dia(here::here('data','dia','StatusQuo_HABhi.dia'))
m.sq <- enforce.limitation(m.sq)


#---- Simulations ---- 
simlist <- readRDS(here('data','HAB_sim_out','HABhi_x_StatusQuo_AllStrat.rds'))

sq.sim <- sqlist[[1]]
```


Read in the simulations / models for the climate adaptation QNMs, for Magel & Francis method.

Parametric insurance ("Insure")
```{r echo=TRUE}
#---- Default Model ---- 
m.insure.habhi <- model.dia(here::here('data','dia','ParametricInsurance_HABhi.dia'))
m.insure.habhi <- enforce.limitation(m.insure.habhi)

#---- Sims ---- 
insure.sim <- simlist[[2]]
```


Existing Fishery Diversification ("Div1")
```{r echo=TRUE}
#---- Default Model ---- 
m.div1 <- model.dia(here::here('data','dia','ExistingFisheriesDiversify_HABhi.dia'))
m.div1 <- enforce.limitation(m.div1)  

#---- Sims ----
div1.sim <- simlist[[3]]
```


New Fishery Diversification ("Div2")
```{r echo=TRUE}
#---- Default Model ---- 
m.div2 <- model.dia(here::here('data','dia','NewFisheries_HABhi.dia'))
m.div2 <- enforce.limitation(m.div2)  


#---- Sims ----
div2.sim <- simlist[[4]]
```


Disaster Relief Spend Plan 1 ("DR1")
```{r echo=TRUE}
#---- Default Model ---- 
m.dr1.habhi <- model.dia(here::here('data','dia','DisasterRelief-1-DirectAssist_HABhi.dia'))
m.dr1.habhi <- enforce.limitation(m.dr1.habhi)


#---- Sims ----
dr1.sim <- simlist[[5]]
```

Disaster Relief Spend Plan 2 ("DR2")
```{r echo=TRUE}
#---- Default Model ---- 
m.dr2.habhi <- model.dia(here::here('data','dia','DisasterRelief-2-MultiObj_HABhi.dia'))
m.dr2.habhi <- enforce.limitation(m.dr2.habhi)


#---- Sims ----
dr2.sim <- simlist[[6]]
```

Supplementary livelihood diversification
```{r echo=TRUE}
#---- Default Model ---- 
m.sdiv.habhi <- model.dia(here::here('data','dia','SupplementaryDiversify_HABhi.dia'))
m.sdiv.habhi <- enforce.limitation(m.sdiv.habhi) 

#---- Sims ----
sdiv.sim <- simlist[[7]]
```

Livelihood diversification with exit - Imposed ("ldiv1") and Invested ("ldiv2")
```{r echo=TRUE}
#---- Default Models ---- 
m.ldiv1.habhi <- model.dia(here::here('data','dia','LivelihoodDiversify-1-Imposed_HABhi.dia'))
m.ldiv1.habhi <- enforce.limitation(m.ldiv1.habhi)  

m.ldiv2.habhi <- model.dia(here::here('data','dia','LivelihoodDiversify-2-Invested_HABhi.dia'))
m.ldiv2.habhi <- enforce.limitation(m.ldiv2.habhi)  


#---- Sims ----
ldiv1.sim <- simlist[[8]]
ldiv2.sim <- simlist[[9]]
```


## Boosted Regression Trees 

Use boosted regression trees to examine the relative importance of model edges (linkages) in determining the response of a given well-being variable to a HAB simulation in the Status Quo model 

First, create a list object to save influence dataframes
```{r}
relinf.list <- list()
```

Then use the custom function `impact.ss` to produce two matrices: (1) the perturbation response (+1/-1/0) of each well-being variable (column) in each simulation iteration (row); and (2) the randomly simulated weight of each edge (column) in each simulation iteration (row). Bind them together.
```{r eval=TRUE}
## two matrices into a list
temp <- impact.ss(sim=sq.sim,perturb=c("HAB"=1),monitor=NA)

## bind together
temp2 <- cbind(temp[[1]],temp[[2]])

## save
write_rds(temp2, here('data','sensitivity','StatusQuo_x_HABhi_GBMin.rds'))
```
```{r echo=FALSE, eval=FALSE}
# read back in
temp2 <- read_rds(here('data','sensitivity','StatusQuo_x_HABhi_GBMin.rds'))
```

### Test 

subset Status Quo response variable set to the variable *Emotional & mental health*. the first 41 cols in the matrix are variables, the remaining are links.
```{r}
d <- cbind(temp2[,"Emotional & mental health"],temp2[,42:(dim(temp2)[2])])  # the first 41 cols are variables, not links
```

Run [gbm.step](https://search.r-project.org/CRAN/refmans/dismo/html/gbm.step.html)
```{r}
fit3 <- gbm.step(data=d,gbm.x=2:121,gbm.y=1,family="gaussian",tree.complexity=5, learning.rate = 0.01,bag.fraction = 0.5)
## save
saveRDS(fit3,file=here('data','sensitivity','StatusQuo_x_HABhi_GBMout_EmotionalMentalHealth.rds'))
```

Use 'summary' to compute the relative influence of each variable in the gbm object. Save to data frame.
```{r}
fit.sq.df <- as.data.frame(summary(fit3), row.names=NULL) %>%
  rename("Link"=var) %>% mutate(Variable="Emotional & mental health") %>%
  rownames_to_column("Link2") %>% dplyr::select(-Link2)

#View fit.sq.df
```



### Status Quo QNM

Look at influential edges (in the Status Quo model) for aspects of well-being that are featured in the main figures of the paper:
```{r}
response.vars <- c("Emotional & mental health",
                   "Shoreside infrastructure & support services",
                   "Subsistence",
                   "Intangible connections to nature",
                   "Identity",
                   "Family",
                   "Community learning & cooperation",
                   "Social relationships",
                   "Community",  # all strong negative except fisheries diversification
                   "Job quality", # did not vary between strategies
                   "Job satisfication", # did not vary between strategies
                   "Material wealth & security") # did not vary between strategies
```

This took awhile on my computer so I did it in two batches.

I start with the second variable because we already did Emotional & Mental Health, in **Test** above. If you didn't run **Test** in the same session, switch which lines are commented out in the code chunk below.
```{r}
start_index <- 2
# start_index <- 1
# fit.sq.df <- data.frame(Link=as.character(),
#                         rel.inf=as.numeric(),
#                         Variable=as.character())
```

Batch 1
```{r}
for(v in response.vars[start_index:8]){
  if(length(unique(temp2[,v])) > 1){
  # Fit classification tree model with the variable
  fit.sq <- gbm.step(data=cbind(temp2[,v],temp2[,42:161]),
                     gbm.x=2:121,gbm.y=1,family="gaussian",tree.complexity=5, learning.rate = 0.01,bag.fraction = 0.5)
  
  # Add to data frame
  fit.sq.df <- fit.sq.df %>%
    bind_rows(as.data.frame(summary(fit.sq), row.names=NULL) %>%
                rename("Link"=var) %>% mutate(Variable=v) %>%
              rownames_to_column("Link2") %>% dplyr::select(-Link2))
  
  rm(fit.sq)
  }
  message("completed variable ", v)
  
  # save final data frame
  write_csv(fit.sq.df, here('data','sensitivity','StatusQuo_x_HABhi_GBMout_1.csv'))
              
}
```

Batch 2
```{r}
for(v in response.vars[10:12]){
  if(length(unique(temp2[,v])) > 1){
  # Fit classification tree model with the variable
  fit.sq <- gbm.step(data=cbind(temp2[,v],temp2[,42:(dim(temp2)[2])]),
                     gbm.x=2:121,gbm.y=1,family="gaussian",tree.complexity=5, learning.rate = 0.01,bag.fraction = 0.5)
  
  # Add to data frame
  
  if(v==response.vars[10]){
    fit.sq.df <- as.data.frame(summary(fit.sq), row.names=NULL) %>%
  rename("Link"=var) %>% mutate(Variable=v) %>%
  rownames_to_column("Link2") %>% dplyr::select(-Link2)
  } else{
  
  fit.sq.df <- fit.sq.df %>%
    bind_rows(as.data.frame(summary(fit.sq), row.names=NULL) %>%
                rename("Link"=var) %>% mutate(Variable=v) %>%
              rownames_to_column("Link2") %>% dplyr::select(-Link2))
  }
  rm(fit.sq)
  }
  message("completed variable ", v)
  
  write_csv(fit.sq.df, here('data','sensitivity','StatusQuo_x_HABhi_GBMout_3.csv'))
              
}
```


Calculate ranks for each of the links, for each variable. save as a matrix.
```{r}
fit.sq.rank <- fit.sq.df %>%
  separate(col="Link", into=c("Edge1","Edge2"), remove=FALSE, sep="_") %>%
  group_by(Variable) %>%
  mutate(rank=dense_rank(desc(rel.inf))) %>%
  dplyr::select(Link,Edge1,Edge2,Variable,rank) %>%
  pivot_wider(names_from="Variable", values_from="rank") %>%
  mutate(rank_sum=rowSums(across(where(is.numeric)))) %>% arrange(rank_sum)

write_csv(fit.sq.rank,file=here('data','sensitivity','StatusQuo_x_HABhi_GBMout_rankSummary.csv'))
```



## Edge Strength

For the Status Quo plus the eight strategy QNMs.

This uses the custom function `qnm_sensitivity`.

Set up:
```{r}
# list of simulations
tmp_sim_list <- list(sq.sim,insure.sim, dr1.sim, dr2.sim, div1.sim, div2.sim, sdiv.sim,ldiv.sim,ldiv2.sim)
# list of models
tmp_mod_list <- list(m.sq, m.insure.habhi,m.dr1.habhi,m.dr2.habhi,m.div1,m.div2,m.sdiv.habhi,m.ldiv.habhi,m.ldiv2.habhi)
# list of simulation names
tmp_names <- c("Status Quo", "Insurance", "Direct Assist Disaster Relief","Multi-0bj Disaster Relief","Fisheries Diversification","New Fisheries","Supplementary Diversification", "Imposed New Livelihoods","Invested New Livelihoods")
# list of perturbations 
tmp_perturbs <- list(c("HAB"),c("HAB","insurance"),
                     c("HAB","disaster relief (direct)"), c("HAB","disaster relief (direct)","disaster relief (invest)"),
                     c("HAB"),c("HAB","New fishery"), c("HAB"),
                     c("HAB"),c("HAB","Transition support"))

sensitivity_all <- list()
```


Run our custom function `qnm_sensitivity` on each simulation / model and save the link weight data frame (`weightdf`), shortest distance dataframe (`distdf`)
```{r}
for(i in seq(1, length(tmp_sim_list))){
  tmpdat <- qnm_sensitivity(dia.mod=tmp_mod_list[[i]], my.sim=tmp_sim_list[[i]], perturb=tmp_perturbs[[i]])
  tmpdist <- tmpdat[[4]]
  tmpweight <- tmpdat[[2]]
  sensitivity_all[[i]] <- tmpdat
  if(i==1){
    distdf <- tmpdist %>% mutate(model=tmp_names[[i]])
    weightdf <- tmpweight %>% mutate(model=tmp_names[[i]])
  } else{
    distdf <- bind_rows(distdf, tmpdist %>% mutate(model=tmp_names[[i]]))
    weightdf <- bind_rows(weightdf, tmpweight %>% mutate(model=tmp_names[[i]]))
  }
}

# names for list of all sensitivity information
names(sensitivity_all) <- tmp_names
```


Start with non-self edges
```{r fig.width=10,fig.height=7}
plotweight <-  weightdf %>% filter(abs(round(Mean,1)) < 0.50 | abs(round(Mean,1)) > 0.50)
plotweight %<>%
  separate(Edge, into=c("edge_1","edge_2"), sep="\\*", remove=FALSE) %>% filter(!is.na(edge_2)) %>%
  mutate(edge_1=str_remove(edge_1," -")) %>%
  bind_rows(plotweight %>%
              separate(Edge, into=c("edge_1","edge_2"), sep="->", remove=FALSE) %>% filter(!is.na(edge_2)) %>%
              mutate(edge_1=str_remove(edge_1," -"),
                     edge_1=str_trim(edge_1,side="both"))) %>%  mutate(edge_2=str_trim(edge_2))  %>%
  mutate(interaction=ifelse(abs(Mean) < 0.50, "weak","strong"),
         interaction_dir=ifelse(Mean<0,"negative","positive"))

outstand_edges1 <- plotweight %>% filter(edge_1 != edge_2) %>%
  mutate(interaction=ifelse(abs(Mean) < 0.50, "weak","strong")) %>%
  group_by(Edge, interaction,interaction_dir) %>%
  summarise(n.mods=length(unique(model))) %>%
  group_by(Edge) %>% mutate(total.mods=sum(n.mods))

ggplot(outstand_edges1,aes(x=Edge,y=n.mods,fill=interaction)) +
  geom_col() + facet_grid(cols=vars(interaction_dir)) +
  coord_flip() +
  labs(x="",y="Number of Models (of 9)") +
  scale_fill_manual(values=c("darkgreen","darkseagreen1")) +
  theme_bw() + theme(axis.text.y=element_text(size=12))
```

Then look at self-edges
```{r}
outstand_edges2 <- plotweight %>% filter(edge_1 == edge_2) %>%
  mutate(interaction=ifelse(abs(Mean) < 0.50, "weak","strong")) %>%
  group_by(Edge, interaction,interaction_dir) %>%
  summarise(n.mods=length(unique(model))) %>%
  group_by(Edge) %>% mutate(total.mods=sum(n.mods))
ggplot(outstand_edges2,aes(x=Edge,y=n.mods,fill=interaction)) +
  geom_col() +
  coord_flip() +
  labs(x="",y="Number of Models (of 9)") +
  scale_fill_manual(values=c("darkgreen","darkseagreen1")) +
  theme_bw() + theme(axis.text.y=element_text(size=12))
```

Save a summary of edges with particularly high interaction strengths; using carryover variable names, which need to be cleaned up for the figure. 
```{r}

strong_edges <- plotweight %>%
  mutate(interaction=ifelse(abs(Mean) < 0.50, "weak","strong")) %>%
  filter(interaction=="strong") %>%
  group_by(Edge, interaction,interaction_dir) %>%
  summarise(n.mods=length(unique(model))) %>%
  group_by(Edge) %>% mutate(total.mods=sum(n.mods)) %>%
  mutate(Edge=str_replace_all(Edge, "Spr/Sum crab","Late season crab")) %>%
  mutate(Edge=str_replace_all(Edge, "Spr/Sum non.crab","Late season other")) %>%
  mutate(Edge=str_replace_all(Edge, "Winter (primary) crab","Early season crab")) %>%
  mutate(Edge=str_replace_all(Edge, "Winter non.crab","Early season other")) %>%
  mutate(Edge=str_replace_all(Edge, "non.crab","other")) %>%
  mutate(Edge=str_replace_all(Edge, "Spr/Sum non.crab","Late season other"))

strong_edges<- strong_edges %>% mutate(Edge=ifelse(Edge=="Winter (primary) crab fishery participation -* Winter (primary) crab fishery participation", "Early season crab fishery participation -* Early season crab fishery participation",
                                                   ifelse(Edge=="Winter (primary) crab fishery participation -* Early season other fishery participation","Early season crab fishery participation -* Early season other fishery participation",Edge)))

strong_edges <- strong_edges %>% mutate(Edge=ifelse(Edge=="disaster relief (direct) -> Material wealth & security",
                                                    "Direct assist (disaster relief) -> Material wealth & security",Edge))

strong_edges <- strong_edges %>% mutate(Edge=ifelse(Edge=="insurance -> Material wealth & security",
                                                    "Insurance pay-out -> Material wealth & security",Edge))


png(here('doc','drafts','supplement','FigS4_StrongEdges_NMods.png'), res=300, width=3200,height=1400)
 ggplot(strong_edges, aes(x=Edge,y=as.integer(n.mods),fill=interaction_dir)) +
  geom_col() + facet_grid(cols=vars(interaction_dir)) +
  coord_flip() +
  labs(x="",y="Number of QNMs") +
  scale_fill_manual(values=c("darkorange","darkgreen"), name="Interaction\n  Direction") +
   scale_y_continuous(breaks=seq(1,10,by=2)) +
  theme_bw() + theme(axis.text.y=element_text(size=12))
dev.off()
```