---
title: "Altering an Influential Link: Early Season Fishing Flexibility"
author: "M Fisher"
date: "run 2023-07-27"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

# Description 

This RMarkdown explores how differences in winter fishing opportunity across communities may affect the outcomes from response strategies to a **high intensity Harmful Algal Bloom.**

Differences in winter fishing opportunity are covered as:

1. Winter crab fishing has an uncertain dampening effect on winter non-crab fishing (STATUS QUO)

2. Winter crab has a certain positive effect on winter crab fishing (*and* remove the restriction that crab Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security) ("WAITING FOR CRAB")

3. Winter crab has a certain negative effect on winter crab fishing ("SWITCHING TARGETS")

4. Winter crab has no effect on winter non-crab fishing ("NO EFFECT")

We can’t know how the behavior of every fisherman in a community will fall out among these three approaches to shifting fishing effort. But we do know that where there is variability, there will be differential outcomes. So we have to understand the relative benefits of an adaptation strategy in the face of this variation, so that we can select a strategy that primarily dampens HAB impacts across community members. 


Structural changes are implemented for the Status Quo QNM and the following strategies:

1. Fisheries insurance

2. Disaster Relief (Spend Plan 1)

3. Disaster Relief (Spend Plan 2)

4. Supplementary Livelihoods Diversification

We don't look at the fisheries diversification strategies because these strategies already involve specific changes to winter fishing trade-offs. 




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)

#---- libraries ----
library(here)
library(tidyverse)
library(ggplot2)
#Load XML first--dependency not included in QPress
#To install QPress: 
#   library(remotes)
#   remotes::install_github("SWotherspoon/QPress")
library(XML)
library(tcltk2)
library(gridExtra)
library(cowplot)
library(QPress)
library(igraph)

#---- custom functions ----
source(here('R','parse.constraints.SWotherspoon.R'))
# source(here('R','impact.table.R'))
source(here('R','compare.baseline.impact.table.R'))
# source(here('R','impact.dataframe.R'))
source(here('R','compare.models.impact.table.R'))

get.score.matrix <- function(x){
  x <- x %>% mutate(model2=ifelse(grepl("---",model),"m1","m0")) %>%
    dplyr::select(variable,model2,response.num) %>% 
    pivot_wider(names_from=model2,values_from=response.num) %>%
    mutate(score=abs(m0-m1)) %>%
    mutate(score=ifelse((m0<0)| (m0==0 & m1<0), score*-1,score))
}



```

## Set up 

how many stable matrices do you want *QPress* to reach? (Fisher et al. uses 10,000; any number up to 50,000 should still take a max of 1-2 minutes per QNM) 
```{r}
nmat <- 10000
```


variable key - this tells the `impact.table` function which variables to report results for, and in what order.
```{r}
sqkey <- read_csv(here('data','sq_variable_key.csv'), col_names=TRUE)
```

sub-select variables to include in figures
```{r}
subvars <- sqkey %>% 
# add a hab variable to the sqkey
  bind_rows(data.frame(variable="HAB",group="ecosystem")) %>%
  filter(group %in% c("well-being","well-being 2","well-being 3","capacity")) %>%
  filter(!(variable %in% c("Physical health","Physical safety","Equity in resource access")))
```

semi-qualitative categories, and color palette
```{r}
score.df <- data.frame(response=c("Negative-Strong","Negative-Weak","Equivocal","Positive-Strong","Positive-Weak","None"),response.num=c(-2,-1,0,2,1,NA))

table.palette.orange <- c("#04BC09", "#ABF1AD","grey85", "#dfc27d","#a6611a","black") # for plotting fx
```

## Status Quo

Default
```{r eval=TRUE}
# dia model
m.sq <- model.dia(here::here('data','dia','StatusQuo_HABhi.dia'))
m.sq <- enforce.limitation(m.sq)

# edge constraints
m.sq.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity"),m.sq)
sq.sampler <- community.ordering.sampler(m.sq.constrained)
```


Waiting for crab
```{r}
# dia model
m.sq.wait <- model.dia(here::here('data','dia','influential_link','StatusQuo_2Wait_HABhi.dia'))
m.sq.wait <- enforce.limitation(m.sq.wait)

# edge constraints
m.sq.wait.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity"),m.sq.wait)
sq.wait.sampler <- community.ordering.sampler(m.sq.wait.constrained)
```

Choose one
```{r}
# dia model
m.sq.one <- model.dia(here::here('data','dia','influential_link','StatusQuo_1Choose_HABhi.dia'))
m.sq.one <- enforce.limitation(m.sq.one)

# edge constraints
m.sq.one.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity"),m.sq.one)
sq.one.sampler <- community.ordering.sampler(m.sq.one.constrained)
```

No effect
```{r}
# dia model
m.sq.no <- model.dia(here::here('data','dia','influential_link','StatusQuo_3NoEffect_HABhi.dia'))
m.sq.no <- enforce.limitation(m.sq.no)

# edge constraints
m.sq.no.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity"),m.sq.no)
sq.no.sampler <- community.ordering.sampler(m.sq.no.constrained)
```


### Simulate a HAB

```{r eval=TRUE}
################# HAB x status quo
sq.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sq, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=sq.sampler,
                            validators=list(press.validate(
                              m.sq,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

################# HAB x status quo - wait for crab
sq.wait.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sq.wait, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=sq.wait.sampler,
                            validators=list(press.validate(
                              m.sq.wait,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

################# HAB x status quo - no effect
sq.no.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sq.no, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=sq.no.sampler,
                            validators=list(press.validate(
                              m.sq.no,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

################# HAB x status quo - choose one
sq.one.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sq.one, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=sq.one.sampler,
                            validators=list(press.validate(
                              m.sq.one,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)
```

output into list
```{r eval=TRUE}
out <- list(sq.sim,sq.wait.sim,sq.no.sim, sq.one.sim)
names(out) <- c("Status Quo","Wait for crab","No effect","Choose one")
saveRDS(out,here('data','HAB_sim_out',paste0('StatusQuo_x_HABhi_',nmat/1000,'k.rds')))
```



### View

read back in
```{r}
sqlist <- readRDS(here('data','HAB_sim_out',paste0('StatusQuo_x_HABhi_',nmat/1000,'k.rds')))

sq.sim <- sqlist[[1]]
sq.wait.sim <- sqlist[[2]]
sq.no.sim <- sqlist[[3]]
sq.one.sim <- sqlist[[4]]
```


```{r  fig.height=6, fig.width=6}
compare.sq.sub <- compare.models.impact.tbl(sim.list=sqlist,
                                         perturb.list=list(c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1)),
                                         monitor.list=list(NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE, table.palette=table.palette.orange)
compare.sq.sub[[3]]
```



## Insurance

### Models

Default
```{r}
# dia model
m.insure <- model.dia(here::here('data','dia','ParametricInsurance_HABhi.dia'))
m.insure <- enforce.limitation(m.insure)

# edge constraints
m.insure.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Winter crab harvest -> Total crab harvest < insurance -> Material wealth & security"),m.insure)
insure.sampler <- community.ordering.sampler(m.insure.constrained)
```

CHOOSE ONE
```{r}
# # dia model
# m.insure.one <- model.dia(here::here('data','dia','influential_link','ParametricInsurance_1Choose_HABhi.dia'))
m.insure.one <- model.dia(here::here('data','dia','influential_link','ParametricInsurance_1Choose_HABhi.dia'))
m.insure.one <- enforce.limitation(m.insure.one)  

# edge constraints
m.insure.one.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                              "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Winter crab harvest -> Total crab harvest < insurance -> Material wealth & security"),m.insure.one)
insure.one.sampler <- community.ordering.sampler(m.insure.one.constrained)
```

WAIT FOR CRAB
```{r}
# dia model
# m.insure.wait <- model.dia(here::here('data','dia','influential_link','ParametricInsurance_2Wait_HABhi.dia'))
m.insure.wait <- model.dia(here::here('data','dia','influential_link','ParametricInsurance_2Wait_HABhi.dia'))
m.insure.wait <- enforce.limitation(m.insure.wait)  

# edge constraints
m.insure.wait.constrained <- parse.constraints(c("Total non.fishing income -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Total non.fishing income -> Material wealth & security < Total non.crab harvest -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Winter crab harvest -> Total crab harvest < insurance -> Material wealth & security"),m.insure.wait)

# m.insure.wait.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
#                                          "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
#                                          "Winter crab harvest -> Total crab harvest < insurance -> Material wealth & security"),m.insure.wait)


insure.wait.sampler <- community.ordering.sampler(m.insure.wait.constrained)
```

NO EFFECT
```{r}
# dia model
# m.insure.no <- model.dia(here::here('data','dia','influential_link','ParametricInsurance_3NoEffect_HABhi.dia'))
m.insure.no <- model.dia(here::here('data','dia','influential_link','ParametricInsurance_3NoEffect_HABhi.dia'))
m.insure.no <- enforce.limitation(m.insure.no)  

# edge constraints
m.insure.no.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Winter crab harvest -> Total crab harvest < insurance -> Material wealth & security"),m.insure.no)
insure.no.sampler <- community.ordering.sampler(m.insure.no.constrained)
```

### Simulate HAB

```{r insur.sim, eval=TRUE}

## LAST RUN 7/24/2023 to simplify interactions with insurance / crab harvest and emotional & mental health

#---- Default ---- 
insure.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.insure, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=insure.sampler,
                            validators=list(press.validate(
                              m.insure,     # the qnm
                              perturb = c(`HAB`=1,
                                          `insurance`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#----- CHOOSE ONE ----
################# simulate HAB
insure.one.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.insure.one, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=insure.one.sampler,
                            validators=list(press.validate(
                              m.insure.one,     # the qnm
                              perturb = c(`HAB`=1,
                                          `insurance`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)


#----- Crab Facilitates ----
################# simulate HAB
insure.wait.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.insure.wait, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=insure.wait.sampler,
                            validators=list(press.validate(
                              m.insure.wait,     # the qnm
                              perturb = c(`HAB`=1,
                                          `insurance`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#----- No Effect ----
################# simulate HAB
insure.no.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.insure.no, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=insure.no.sampler,
                            validators=list(press.validate(
                              m.insure.no,     # the qnm
                              perturb = c(`HAB`=1,
                                          `insurance`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)
```

save
```{r}
insure_list <- list(insure.sim,insure.one.sim,insure.wait.sim, insure.no.sim)
names(out) <- c("Default","Choose one","Wait for crab","No effect")
saveRDS(out,here('data','HAB_sim_out',paste0('Insurance_x_HABhi_',nmat/1000,'k.rds')))
```


### View

read back in
```{r}
insure_list <- readRDS(here('data','HAB_sim_out',paste0('Insurance_x_HABhi_',nmat/1000,'k.rds')))
names(insure_list)
insure_list <- list(insure_list[[1]], insure_list[[4]], insure_list[[2]], insure_list[[3]])
names(insure_list) <- c("Default","Choose one","Wait for crab","No effect")
```


```{r fig.height=6, fig.width=6}
compare.insure.sub <- compare.models.impact.tbl(sim.list=insure_list,
                                         perturb.list=list(c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`insurance`=1)),
                                         monitor.list=list(NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE, table.palette=table.palette.orange)
compare.insure.sub[[3]]
```




## Disaster Relief 1

### Models

Default
```{r}
#---- Model with HAB ---- 
# dia model
m.dr1 <- model.dia(here::here('data','dia','DisasterRelief-1-DirectAssist_HABhi.dia'))
m.dr1 <- enforce.limitation(m.dr1)

# edge constraints
m.dr1.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr1)
dr1.sampler <- community.ordering.sampler(m.dr1.constrained)
```

CHOOSE ONE
```{r}
# dia model
m.dr1.one.habhi <- model.dia(here::here('data','dia','influential_link','DisasterRelief-1-DirectAssist_1Choose_HABhi.dia'))
m.dr1.one.habhi <- enforce.limitation(m.dr1.one.habhi)

# edge constraints
m.dr1.one.habhi.constrained <- parse.constraints(c("Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr1.one.habhi)
dr1.one.habhi.sampler <- community.ordering.sampler(m.dr1.one.habhi.constrained)
```

WAIT FOR CRAB
```{r}
# dia model
m.dr1.wait <- model.dia(here::here('data','dia','influential_link','DisasterRelief-1-DirectAssist_2Wait_HABhi.dia'))
m.dr1.wait <- enforce.limitation(m.dr1.wait)

# edge constraints
m.dr1.wait.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr1.wait)
dr1.wait.sampler <- community.ordering.sampler(m.dr1.wait.constrained)
```

NO EFFECT
```{r}
# dia model
m.dr1.no <- model.dia(here::here('data','dia','influential_link','DisasterRelief-1-DirectAssist_3NoEffect_HABhi.dia'))
m.dr1.no <- enforce.limitation(m.dr1.no)

# edge constraints
m.dr1.no.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr1.no)
dr1.no.sampler <- community.ordering.sampler(m.dr1.no.constrained)
```


### Simulate HAB

```{r dr1.sim, eval=TRUE}
#---- Default Model with HAB ---- 
##### Simulate a HAB
dr1.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr1, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr1.sampler,
                            validators=list(press.validate(
                              m.dr1,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#---- CHOOSE ONE ----
##### Simulate a HAB
dr1.one.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr1.one.habhi, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr1.one.habhi.sampler,
                            validators=list(press.validate(
                              m.dr1.one.habhi,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#---- WAIT FOR CRAB ----
##### Simulate a HAB
dr1.wait.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr1.wait, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr1.wait.sampler,
                            validators=list(press.validate(
                              m.dr1.wait,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#---- NO EFFECT ---- 
##### Simulate a HAB 
dr1.no.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr1.no, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr1.no.sampler,
                            validators=list(press.validate(
                              m.dr1.no,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)
```

save
```{r}
dr1_list <- list(dr1.sim, dr1.one.sim,dr1.wait.sim,dr1.no.sim)
names(dr1_list) <- c("Default","Choose one","Wait for crab","No effect")
saveRDS(dr1_list,here('data','HAB_sim_out',paste0('DisasterRelief1_x_HABhi_', nmat/1000,'k.rds')))
# saveRDS(dr1_list,here('data','HAB_sim_out','DisasterRelief1_x_HABhi_50k.rds')) # will overwrite
```


### View
read back in
```{r}
dr1_list <- readRDS(here('data','HAB_sim_out',paste0('DisasterRelief1_x_HABhi_', nmat/1000,'k.rds')))
```


```{r  fig.height=6, fig.width=6}
compare.dr1.sub <- compare.models.impact.tbl(sim.list=dr1_list,
                                         perturb.list=list(c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1)),
                                         monitor.list=list(NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE, table.palette=table.palette.orange)
compare.dr1.sub[[3]]
```




## Disaster Relief 2

### Models

Default Model with HAB 
```{r}
# dia model
m.dr2 <- model.dia(here::here('data','dia','DisasterRelief-2-MultiObj_HABhi.dia'))
m.dr2 <- enforce.limitation(m.dr2)

# edge constraints
m.dr2.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr2)
dr2.sampler <- community.ordering.sampler(m.dr2.constrained)
```

CHOOSE ONE 
```{r}
# dia model
m.dr2.one <- model.dia(here::here('data','dia','influential_link','DisasterRelief-2-MultiObj_1Choose_HABhi.dia'))
m.dr2.one <- enforce.limitation(m.dr2.one)

# edge constraints
m.dr2.one.constrained <- parse.constraints(c("Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr2.one)
dr2.one.sampler <- community.ordering.sampler(m.dr2.one.constrained)
```

WAIT FOR CRAB
```{r}
# dia model
m.dr2.wait <- model.dia(here::here('data','dia','influential_link','DisasterRelief-2-MultiObj_2Wait_HABhi.dia'))
m.dr2.wait <- enforce.limitation(m.dr2.wait)

# edge constraints
m.dr2.wait.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr2.wait)
dr2.wait.sampler <- community.ordering.sampler(m.dr2.wait.constrained)
```

NO EFFECT 
```{r}
# dia model
m.dr2.no <- model.dia(here::here('data','dia','influential_link','DisasterRelief-2-MultiObj_3NoEffect_HABhi.dia'))
m.dr2.no <- enforce.limitation(m.dr2.no)

# edge constraints
m.dr2.no.constrained <- parse.constraints(c("Total non.crab harvest -> Material wealth & security < Total crab harvest -> Material wealth & security",
                                         "Non.crab fishing activity -> Identity < Crab fishing activity -> Identity",
                                         "Total crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security",
                                         "Total non.crab harvest -> Material wealth & security < disaster relief (direct) -> Material wealth & security"),m.dr2.no)
dr2.no.sampler <- community.ordering.sampler(m.dr2.no.constrained)
```


### Simulate HAB

```{r dr2.sim, eval=TRUE}
#---- default Model with HAB ---- 
#### Simulate a HAB 
dr2.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr2, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr2.sampler,
                            validators=list(press.validate(
                              m.dr2,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1,
                                          `disaster relief (invest)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#---- CHOOSE ONE ----
##### Simulate a HAB
dr2.one.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr2.one, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr2.one.sampler,
                            validators=list(press.validate(
                              m.dr2.one,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1,
                                          `disaster relief (invest)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#---- WAIT FOR CRAB ----
##### Simulate a HAB
dr2.wait.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr2.wait, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr2.wait.sampler,
                            validators=list(press.validate(
                              m.dr2.wait,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1,
                                          `disaster relief (invest)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)

#---- NO EFFECT ---- 
##### Simulate a HAB 
dr2.no.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.dr2.no, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=dr2.no.sampler,
                            validators=list(press.validate(
                              m.dr2.no,     # the qnm
                              perturb = c(`HAB`=1,
                                          `disaster relief (direct)`=1,
                                          `disaster relief (invest)`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)
```

save
```{r}
dr2_list <- list(dr2.sim,dr2.one.sim, dr2.wait.sim,dr2.no.sim)
names(dr2_list) <- c("Default","Choose one","Wait for crab","No effect")
saveRDS(dr2_list,here('data','HAB_sim_out',paste0('DisasterRelief2_x_HABhi_', nmat/1000,'k.rds')))
```

### View

read back in
```{r}
dr2_list <- readRDS(here('data','HAB_sim_out',paste0('DisasterRelief2_x_HABhi_', nmat/1000,'k.rds')))
```

```{r  fig.height=6, fig.width=6}
names(dr2_list) <- c("Default","Choose one","Wait for crab","No effect")
compare.dr2.sub <- compare.models.impact.tbl(sim.list=dr2_list,
                                         perturb.list=list(c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1)),
                                         monitor.list=list(NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE, table.palette=table.palette.orange)
compare.dr2.sub[[3]]
```


## Supplementary Livelihoods

This strategy has a slightly different approach to variability in winter fishing opportunities.

The default implementation is structured so that winter crab fishing has (1) an uncertain dampening effect on winter non-crab fishing, and (2) a dampening effect on non-fishing employment. Non-fishing employment and winter non-crab fishing have a two-way dampening effect.

### Models

Default
```{r}
# --- default ---
# dia model
m.sdivS <- model.dia(here::here('data','dia','SupplementaryDiversify_HABhi.dia'))
m.sdivS <- enforce.limitation(m.sdivS)  

# no edge constraints
```


Choose one
```{r}
# dia model
m.sdivS.one <- model.dia(here::here('data','dia','influential_link','SupplementaryDiversify_1Choose_HABhi.dia'))
m.sdivS.one <- enforce.limitation(m.sdivS.one)  

# no edge constraints
```

Wait for crab
```{r}
# dia model
m.sdivS.wait <- model.dia(here::here('data','dia','influential_link','SupplementaryDiversify_2Wait_HABhi.dia'))
m.sdivS.wait <- enforce.limitation(m.sdivS.wait)  

# no edge constraints
```

crab has no effect
```{r}
# dia model
m.sdivS.no <- model.dia(here::here('data','dia','influential_link','SupplementaryDiversify_3NoEffect_HABhi.dia'))
m.sdivS.no <- enforce.limitation(m.sdivS.no)  

# no edge constraints
```


### Simulate a HAB
```{r sdiv.sim, eval=TRUE}
################# HAB x default
sdivS.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sdivS, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=community.sampler(m.sdivS, required.groups = c(0)),
                            validators=list(press.validate(
                              m.sdivS,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)


#---- choose one ---
################# HAB
sdivS.one.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sdivS.one, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=community.sampler(m.sdivS.one, required.groups = c(0)),
                            validators=list(press.validate(
                              m.sdivS.one,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)


#---- wait for crab ---
################# HAB
sdivS.wait.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sdivS.wait, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=community.sampler(m.sdivS.wait, required.groups = c(0)),
                            validators=list(press.validate(
                              m.sdivS.wait,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)


#---- crab has no effect ---
################# HAB
sdivS.no.sim <- system.simulate(n.sims=nmat, # number of randomly generated matrices to keep
                            edges=m.sdivS.no, # the qnm
                            required.groups = c(0), # allow uncertain edges
                            sampler=community.sampler(m.sdivS.no, required.groups = c(0)),
                            validators=list(press.validate(
                              m.sdivS.no,     # the qnm
                              perturb = c(`HAB`=1), # the perturbation
                              monitor = NA))) # a list of expected outcomes that should happen in the simulation (I don't usually use this)
```


save
```{r}
sdiv_list <- list(sdivS.sim, sdivS.one.sim,sdivS.wait.sim,sdivS.no.sim)
names(sdiv_list) <- c("Default","Choose one","Wait for crab","No effect")
saveRDS(sdiv_list,here('data','HAB_sim_out',paste0('SupplementaryDiv_x_HABhi_', nmat/1000,'k.rds')))
```

### View

read back in
```{r}
sdiv_list <- readRDS(here('data','HAB_sim_out',paste0('SupplementaryDiv_x_HABhi_', nmat/1000,'k.rds')))
```

```{r fig.height=6, fig.width=6}
names(sdiv_list) <- c("Default","Choose one","Wait for crab","No effect")
compare.sdiv.sub <- compare.models.impact.tbl(sim.list=sdiv_list,
                                         perturb.list=list(c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1)),
                                         monitor.list=list(NA,NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE, table.palette=table.palette.orange)
compare.sdiv.sub[[3]]
```


## Visualize Across Strat

Use more extensive visualizations than presented in the paper to determine:
Are there commonalities across strategies when we change the *uncertain* dampening relationship between winter crab and non-crab fishing to...

### Switching targets

a *certain* dampening relationship. more crab = less non-crab
```{r  fig.height=6, fig.width=8}
tmp_list <- list(sq.sim, sq.one.sim, insure.sim,insure.one.sim,
                 dr1.sim,dr1.one.sim,
                 dr2.sim,dr2.one.sim,
                 sdivS.sim,sdivS.one.sim); names(tmp_list) <- c("Status Quo", " ---Switch Target SQ",
                                                                          "Insurance Default"," ---Switch Target I",
                                                                          "Disaster Relief 1 Default"," ---Switch Target DR1",
                                                                          "Disaster Relief 2 Default"," ---Switch Target DR2",
                                                                          "Supp Diverse Default"," ---Switch Target SDIV")
compare.alt1.sub <- compare.models.impact.tbl(sim.list=tmp_list,
                                         perturb.list=list(c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1)),
                                         monitor.list=list(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE, table.palette=table.palette.orange)
compare.alt1.sub[[3]] + geom_vline(aes(xintercept=2.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=4.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=6.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=8.5), linewidth=1.5)
```


```{r message=FALSE, warning=FALSE}
score.df <- data.frame(response=c("Negative-Strong","Negative-Weak","Equivocal","Positive-Strong","Positive-Weak","None"),response.num=c(-2,-1,0,2,1,NA))
trial <- compare.alt1.sub[[1]] %>% left_join(score.df,by="response") %>% dplyr::select(variable,response,node_to_perturb,model,response.num) %>%
   mutate(group=ifelse(grepl("Status Quo",model) | grepl("SQ",model), "SQ",
                       ifelse(grepl("Insur",model) | grepl("Dampens I",model),"Insure",
                              ifelse(grepl("Relief 1",model) | grepl("DR1",model),"DR1",
                                     ifelse(grepl("Relief 2",model) | grepl("DR2",model),"DR2",
                                            ifelse(grepl("Supp",model) | grepl("SDIV",model),"SDIV",NA))))))

trial.nested <- trial %>% group_by(group) %>% nest()
trial.nested$data.scored <- map(trial.nested$data,get.score.matrix)

trial.unnested <- trial.nested %>% unnest(cols=c(group,data.scored)) %>% dplyr::select(-data) %>%
  left_join(score.df,by=c("m0"="response.num")) %>%
  rename(Default=response) %>% rename(response=score)

trial.unnested <- left_join(trial.unnested, trial %>% dplyr::select(group,variable,node_to_perturb) %>% distinct())

plotdat <- trial.unnested %>% mutate(response=ifelse(node_to_perturb=="y","Perturbed",response)) %>%
  mutate(no_input=ifelse(is.na(response),"None",NA)) %>% filter(response != "Perturbed") %>%
  mutate(group=ifelse(group=="SQ", "Status Quo",
                      ifelse(group=="DR1","Disaster Relief 1",
                             ifelse(group=="DR2","Disaster Relief 2",
                                    ifelse(group=="Insure","Insurance",
                                           ifelse(group=="SDIV","Supp Div")))))) %>%
  filter()

var_order <- subvars %>% arrange(specific_order) %>% pull(variable)
    
    plotdat$response <- factor(plotdat$response, levels=c("2","1","0","-1","-2"))
    plotdat$variable <- factor(plotdat$variable, levels=rev(var_order))
    plotdat$group <- factor(plotdat$group,levels=c("Status Quo","Insurance","Disaster Relief 1","Disaster Relief 2","Supp Div"))
```   


Since it's a little difficult to look at variable change between model pairs, lets code that change and plot it. (0 = no change, -1 = drop one level, +1 = up one level)
```{r}
with(plotdat, table(group,response))
```







### Waiting for crab

an amplifying relationship (more crab = more non-crab)
```{r  fig.height=6, fig.width=7}
tmp_list <- list(sq.sim, sq.wait.sim,
                 insure.sim,insure.wait.sim,
                 dr1.HABhi.sim,dr1.wait.sim,
                 dr2.HABhi.sim,dr2.wait.sim,
                 sdivS.sim,sdivS.wait.sim); names(tmp_list) <- c("Status Quo", " ---Wait for Crab SQ",
                                                                         "Insurance Default"," ---Wait for Crab Insure",
                                                                          "Disaster Relief 1 Default"," ---Wait for Crab DR1",
                                                                          "Disaster Relief 2 Default"," ---Wait for Crab DR2",
                                                                          "Supp Diverse Default"," ---Wait for Crab SDIV")
compare.alt2.sub <- compare.models.impact.tbl(sim.list=tmp_list,
                                         perturb.list=list(c(`HAB`=1), c(`HAB`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1)),
                                         monitor.list=list(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE)
compare.alt2.sub[[3]] + geom_vline(aes(xintercept=2.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=4.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=6.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=8.5), linewidth=1.5)
```

```{r message=FALSE, warning=FALSE}
trial <- compare.alt2.sub[[1]] %>% left_join(score.df,by="response") %>% dplyr::select(variable,response,node_to_perturb,model,response.num) %>%
   mutate(group=ifelse(grepl("Status Quo",model) | grepl("SQ",model), "SQ",
                       ifelse(grepl("Insur",model),"Insure",
                              ifelse(grepl("Relief 1",model) | grepl("DR1",model),"DR1",
                                     ifelse(grepl("Relief 2",model) | grepl("DR2",model),"DR2",
                                            ifelse(grepl("Supp",model) | grepl("SDIV",model),"SDIV",NA))))))

trial.nested <- trial %>% group_by(group) %>% nest()
trial.nested$data.scored <- map(trial.nested$data,get.score.matrix)

trial.unnested <- trial.nested %>% unnest(cols=c(group,data.scored)) %>% dplyr::select(-data) %>%
  left_join(score.df,by=c("m0"="response.num")) %>%
  rename(Default=response) %>% rename(response=score)

trial.unnested <- left_join(trial.unnested, trial %>% dplyr::select(group,variable,node_to_perturb) %>% distinct())

plotdat <- trial.unnested %>% mutate(response=ifelse(node_to_perturb=="y","Perturbed",response)) %>%
  mutate(no_input=ifelse(is.na(response),"None",NA)) %>% filter(response != "Perturbed") %>%
  mutate(group=ifelse(group=="SQ", "Status Quo",
                      ifelse(group=="DR1","Disaster Relief 1",
                             ifelse(group=="DR2","Disaster Relief 2",
                                    ifelse(group=="Insure","Insurance",
                                           ifelse(group=="SDIV","Supp Div")))))) %>%
  filter()

var_order <- subvars %>% arrange(specific_order) %>% pull(variable)
    
    plotdat$response <- factor(plotdat$response, levels=c("2","1","0","-1","-2"))
    plotdat$variable <- factor(plotdat$variable, levels=rev(var_order))
    plotdat$group <- factor(plotdat$group,levels=c("Status Quo","Insurance","Disaster Relief 1","Disaster Relief 2","Supp Div"))
```   

Since it's a little difficult to look at variable change between model pairs, lets code that change and plot it. (0 = no change, -1 = drop one level, +1 = up one level)
```{r fig.height=5, fig.width=5}
ggplot(plotdat) + 
      geom_point(aes(y=variable,x=group,fill=response),pch=22,size=8,color="grey60") +
      geom_point(aes(y=variable,x=group,pch=as.factor(no_input)),size=7,color="grey60") +
      geom_text(aes(y=variable,x=group,label=response)) +
      labs(x="",y="") + 
      scale_fill_manual(name="Change",values=table.palette, drop=FALSE, na.translate=FALSE) +
      scale_shape_manual(name="",values=c(0),na.translate=FALSE) +
      scale_x_discrete(position = "top",expand = c(0.1, 0.1)) +
      theme_bw() + theme(axis.text.x=element_text(angle=45,hjust=0))
```


```{r}
with(plotdat, table(group,response))

plotdat %>% dplyr::select(group,response,variable) %>%
  mutate(variable=paste0("var-",variable)) %>%
  pivot_wider(names_from=variable,values_from=response) %>%
  pivot_longer(cols=starts_with('var'), names_to="variable",values_to="response") %>% 
  count(group,response) %>%  mutate(freq = n / sum(n)) %>% dplyr::select(-n) %>%
  pivot_wider(names_from=response, values_from=freq)
```




### No Effect

no relationship 
```{r  fig.height=6, fig.width=7}
tmp_list <- list(sq.sim, sq.no.sim,
                 insure.sim,insure.no.sim,
                 dr1.HABhi.sim,dr1.no.sim,
                 dr2.HABhi.sim,dr2.no.sim,
                 sdivS.sim,sdivS.no.sim); names(tmp_list) <- c("Status Quo", " ---No Effect SQ",
                                                                           "Insurance Default"," ---No Effect Insure",
                                                                          "Disaster Relief 1 Default"," ---No Effect DR1",
                                                                          "Disaster Relief 2 Default"," ---No Effect DR2",
                                                                          "Supp Diverse Default"," ---No Effect SDIV")
compare.alt3.sub <- compare.models.impact.tbl(sim.list=tmp_list,
                                         perturb.list=list(c(`HAB`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`insurance`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1,`disaster relief (direct)`=1,`disaster relief (invest)`=1),
                                                           c(`HAB`=1),
                                                           c(`HAB`=1)),
                                         monitor.list=list(NA,NA,NA,NA,NA,NA,NA,NA,NA,NA),
                                    strong_lower=0.8, weak_lower=0.6, epsilon=1.0E-5,
                                    variable.key = subvars, variable.order="specific_order",plot=TRUE)
compare.alt3.sub[[3]] + geom_vline(aes(xintercept=2.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=4.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=6.5), linewidth=1.5) + 
  geom_vline(aes(xintercept=8.5), linewidth=1.5)
```

```{r message=FALSE, warning=FALSE}
trial <- compare.alt3.sub[[1]] %>% left_join(score.df,by="response") %>% dplyr::select(variable,response,node_to_perturb,model,response.num) %>%
   mutate(group=ifelse(grepl("Status Quo",model) | grepl("SQ",model), "SQ",
                       ifelse(grepl("Insur",model),"Insure",
                              ifelse(grepl("Relief 1",model) | grepl("DR1",model),"DR1",
                                     ifelse(grepl("Relief 2",model) | grepl("DR2",model),"DR2",
                                            ifelse(grepl("Supp",model) | grepl("SDIV",model),"SDIV",NA))))))

trial.nested <- trial %>% group_by(group) %>% nest()
trial.nested$data.scored <- map(trial.nested$data,get.score.matrix)

trial.unnested <- trial.nested %>% unnest(cols=c(group,data.scored)) %>% dplyr::select(-data) %>%
  left_join(score.df,by=c("m0"="response.num")) %>%
  rename(Default=response) %>% rename(response=score)

trial.unnested <- left_join(trial.unnested, trial %>% dplyr::select(group,variable,node_to_perturb) %>% distinct())

plotdat <- trial.unnested %>% mutate(response=ifelse(node_to_perturb=="y","Perturbed",response)) %>%
  mutate(no_input=ifelse(is.na(response),"None",NA)) %>% filter(response != "Perturbed") %>%
  mutate(group=ifelse(group=="SQ", "Status Quo",
                      ifelse(group=="DR1","Disaster Relief 1",
                             ifelse(group=="DR2","Disaster Relief 2",
                                    ifelse(group=="Insure","Insurance",
                                           ifelse(group=="SDIV","Supp Div")))))) %>%
  filter()

var_order <- subvars %>% arrange(specific_order) %>% pull(variable)
    
    plotdat$response <- factor(plotdat$response, levels=c("2","1","0","-1","-2"))
    plotdat$variable <- factor(plotdat$variable, levels=rev(var_order))
    plotdat$group <- factor(plotdat$group,levels=c("Status Quo","Insurance","Disaster Relief 1","Disaster Relief 2","Supp Div"))
```   
Since it's a little difficult to look at variable change between model pairs, lets code that change and plot it. (0 = no change, -1 = drop one level, +1 = up one level)
```{r}
with(plotdat, table(group,response))

plotdat %>% dplyr::select(group,response,variable) %>%
  mutate(variable=paste0("var-",variable)) %>%
  pivot_wider(names_from=variable,values_from=response) %>%
  pivot_longer(cols=starts_with('var'), names_to="variable",values_to="response") %>% 
  count(group,response) %>%  mutate(freq = n / sum(n)) %>% dplyr::select(-n) %>%
  pivot_wider(names_from=response, values_from=freq)
```









